The Role of Ice Compositions and Morphology for Snowlines and the C/N/O Ratios in Active Disks

### 2016-03-09 tex/draft2/ms_edited.tex
update

Changes in stellar luminosity (e.g., \citealt{kennedy06}) and gas mass accretion rate (e.g., \citealt{chambers09}), as well as the evolution of icy dust particles due to grain growth and fragmentation (e.g., \citealt{birnstiel12}), may introduce additional uncertainties in the snowline locations, and thus the C/N/O ratios. Given the number of uncertainties in snowline locations, detections of snowlines in a sample of disks at different evolutionary stages are needed to provide observational constraints. Current detections include the H$_2$O snowline in TW Hya \citep{zhang13} and the CO snowline in TW Hya \citep{qi13} and HD 163296 \citep{qi15}. However, more snowline detections in disks of different ages are expected in future ALMA cycles.

>>>>

Changes in stellar luminosity (e.g., \citealt{kennedy06}) and gas mass accretion rate (e.g., \citealt{chambers09}), as well as the evolution of icy dust particles due to grain growth and fragmentation (e.g., \citealt{birnstiel12}), may introduce additional uncertainties in the snowline locations, and thus the C/N/O ratios. Given the number of uncertainties in snowline locations, detections of snowlines in a sample of disks at different evolutionary stages are needed to provide observational constraints. Current detections include the H$_2$O snowline in TW Hya \citep{zhang13} and the CO snowline in TW Hya \citep{qi13} and HD 163296 \citep{qi15}. More snowline detections in disks of different ages are expected in future ALMA cycles.  Snowline observations may also be used to constrain the degree of turbulence in protoplanetary disks \citep{owen14}. We note, however, that observations of snowlines may not be enough to break the degeneracies in snowline locations produced by disk dynamics, ice morphology, and other effects outlined above. For example, a detection of the CO snowline at a temperature higher than the assumed desorption temperature in a static disk with CO as pure ice ($\sim$17 K, e.g. \citealt{qi13}) could be caused either by CO being in a water dominated environment or by dynamical effects that push the CO snowline inward. This degeneracy can be broken in extreme cases --- for our fiducial disk model, this implies a detection of a CO snowline close to $\sim$9 AU or $\sim$61 AU (see Section \ref{sec:dynamic}).
